Lessons learned and paths forward for rabies dog vaccination in Madagascar: a case study of pilot vaccination campaigns in Moramanga District

### 2021-02-20 paper/mdpi_paper.Rmd
updated output files

    affil: 1, *

@@

    affil: 2, *

@@

authorcontributions: |
  Conceptualization, MR, KV, JL, TS, ZF, GE; methodology, MR, KV, JL, TS, ZF, GE, KH, CJEM, AY; data collection: MR, ZR, CH, RRR, GE, MA, NPR, JN, AF, TR, FD; formal analysis, MR, CF, AY; writing—original draft preparation, CF, MR; writing—review and editing, CF, MR, CJEM, TC, ZF, KV, KH, GE, CH; visualization, MR; supervision, KV, KH, CJEM, ZF; project administration, MR, ZR, CH, RRR, GE, MA, NPR, JN, AF, TR, FD, KV, ZF; funding acquisition, MR, KV, JL, TS, ZF, TC. 

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, 
                      message=FALSE, out.width="80%")
library(tidyverse)
library(glue)
library(magrittr)
library(lubridate)
library(sf)
library(gt)
library(here)
source("R/dem_models.R")

>>>>

    affil: 1, \dagger

@@

    affil: 2, \dagger

@@

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, 
                      message=FALSE, out.width="80%")
library(tidyverse)
library(glue)
library(magrittr)
library(lubridate)
library(sf)
library(gt)
library(here)
source(here("R/dem_models.R"))
